Collaborative Visual Analysis on the Web with RCloud

### 2015-06-26 relatedwork.tex
EDA in JavaScript is absurd

\paragraph*{Web-based tools for sharing code snippets}
Quite a few tools were recently developed for quickly
sharing small programs on the web, including
bl.ocks~\cite{blocks}, jsfiddle~\cite{jsfiddle}, and
plot.ly~\cite{plotly}. bl.ocks and jsfiddle are designed to
share Javascript programs, which means that deployment happens
automatically through the web browser. If Javascript becomes
the lingua franca of exploratory data analysis, we foresee
building a simpler version of RCloud where all execution happens
either on the client side or via web services. Unfortunately that is
not realistic today, making these stand-alone
solutions unsuitable for our purpose. Plot.ly is notable in that it
provides API support for publishing \emph{from} scripts: 
it is possible to generate a plot.ly visualization within
another program. Although this is an intriguing idea, it
nevertheless creates a disconnection between the analysis and the
resulting visualization. In RCloud, we wanted to ensure that every
visualization is transparently linked to the source code that
generates it.

>>>>

\paragraph*{Web-based tools for sharing code snippets}
Quite a few tools were recently developed for quickly
sharing small programs on the web, including
bl.ocks~\cite{blocks}, jsfiddle~\cite{jsfiddle}, and
plot.ly~\cite{plotly}. bl.ocks and jsfiddle are designed to
share Javascript programs, which means that deployment happens
automatically through the web browser. This provides a seamless
way to share visualization techniques, but it does not help with
analysis.
%% If Javascript becomes
%% the lingua franca of exploratory data analysis, we foresee
%% building a simpler version of RCloud where all execution happens
%% either on the client side or via web services. Unfortunately that is
%% not realistic today, making these stand-alone
%% solutions unsuitable for our purpose. 
Plot.ly is notable in that it
provides API support for publishing \emph{from} scripts: 
it is possible to generate a plot.ly visualization within
another program. Although this is an intriguing idea, it
nevertheless creates a disconnection between the analysis and the
resulting visualization. In RCloud, we wanted to ensure that every
visualization is transparently linked to the source code that
generates it.
